Data Preparation

### 2019-01-09 Data Preparation.Rmd
renames transcript variables

```

>>>>

```
##Student Data
###Renaming Variables
First we rename the variable names to make them more comprehensible:
```{r}
d_rename <-d_dirt %>%
  rename(
    ID                     =  "X...Student.Number", 
    Code                   =  "Module..Abbrev..", 
    `Course Title`         =  "Module..Desc..",
    `Program Abbreviation` =  "Program..Abbreviation.", 
    `Program Description`  =  "Program..Description.",               
    Year                   =  "Academic.Year",                      
    Session                =  "Academic.Session",
    `Appraisal Code`       =  "Appraisal.Type",                     
    `Appraisal Title`      =  "Appraisal..Description.",             
    Attempt                =  "Number.rep..attemp",                 
    Grade                  =  "Grade.symbol",                        
    `Appraisal Status`     =  "Appraisal.Status",                   
    `Appraisal Status Description` =  "Appraisal.Status..Desc..",    #is only NA: unique(d4$Appraisal.Status..Desc..)       
    `Booking Reason`       =  "Module.Booking.Reason..Description.",
    `Appraisal Date`       =  "Appraisal.date",                      
    `Attempted Credits`    =  "Attempted.credits",                  
    `Earned Credit`        =  "Earned.Credits",                      
    `Credit Type`          =  "Credit.Type",                        
    `Personnel Number`     =  "Personnel.Number",                  
    `Name (Employee/Applicant)`=  "Name.of.employee.or.applicant",      
    `Individual Work`      =  "Individual.Work",                     
    `Academic Work ID`     =  "Academic.Work.ID",                   
    `Booking Status`       =  "Booking.Status",                      #empty
    `Booking Status Description` =  "Booking.Status..Desc..",             
    `Event Object Id`      =  "Event.Object.Id",                     #empty forwards and including      
    `Business Event Abbreviation` =  "Business.event.abbr.",               
    `Event Description`    =  "Event.Description",                   
    `Start time`           =  "Start.time",                         
    `End time`             =  "End.time",                            
    `Date`                 =  "Date",                               
    `Studyplan`            =  "Studyplan",                           
    `Conditional booking`  =  "Conditiona.booking",                 
    `Wachtlist`            =  "Wachtlist",                           
    `Object ID`            =  "Object.ID",                          
    `Object Name`          =  "Object.name",                         
    `Start Date`           =  "Start.date",                         
    `End Date`             =  "End.Date",                            
    `Number of Weeks`      =  "Number.of.weeks",                      #until this one next has values              
    `Appraiser ID`         =  "Appraiser.ID",                        
    `Appraiser Name`       =  "Appraiser.Name"

  ) 
```

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
